---
title: "Disconnected Landlords PSM Analysis"
author: "Dmytro Kunchenko"
date: "2025-06-04"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
# This chunk runs setup code but doesn't show in the document.
# Load required packages
library(fixest)
library(car) 
library(httr) 
library(jsonlite) 
library(data.table)
library(MatchIt)
library(cobalt)
library(optmatch) 
library(Matching) 
library(rgenoud) 
library(marginaleffects)
library(ggplot2)
library(gridExtra) 
library(kableExtra)
library(rlang) # For handling expressions in the function

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,      # Hide R code by default
  cache = FALSE, 
  message = FALSE,   # Suppress messages
  warning = FALSE,   # Suppress warnings
  fig.height = 6,
  fig.width = 10,
  include = TRUE     # Include output (plots, tables) by default
)
```

# Overview

This document outlines the Propensity Score Matching (PSM) analysis conducted for the "Disconnected Landlords" project. It includes data loading, cleaning, treatment definitions, matching procedures, balance diagnostics, and regression analyses. This version has been refactored to improve conciseness and reduce code duplication by splitting the main analysis function.

# Data Loading and Preprocessing

## Load Data

First, load the dataset. **Ensure the path to the .RData file is correct.**

```{r load_data, echo=TRUE}
# Load data
# Replace with the correct path if necessary
load_path <- "~/disconnected-landlords-project/EPC_matched_combined.RData" 
# For testing, if the file doesn't exist, create a dummy EPC_matched_combined
if (!file.exists(load_path)) {
  warning(paste("Data file not found at:", load_path, ". Using a minimal dummy dataset for demonstration."))
  EPC_matched_combined <- data.table(
    UPRN = 1:1000,
    MAIN_FUEL = sample(c("mains gas", "electricity", "oil", "Gas: mains gas", "INVALID!", "", "To be used only when other fuel specified"), 1000, replace = TRUE),
    country_incorporated_1 = sample(c("UNITED KINGDOM", "JERSEY", "USA"), 1000, replace = TRUE),
    coarse_proprietorship = sample(c("For-Profit", "Non-Profit", "Public Sector", "Individual"), 1000, replace = TRUE),
    country_incorporated_tax_haven = sample(c(0, 1, NA), 1000, replace = TRUE, prob = c(0.7, 0.2, 0.1)),
    tenure = sample(c("Freehold", "Leasehold", NA), 1000, replace = TRUE),
    CONSTRUCTION_AGE_BAND = sample(c("2000-Present", "1950-1975", "Pre-1900", NA), 1000, replace = TRUE),
    PROPERTY_TYPE = sample(c("House", "Flat", "Bungalow", NA), 1000, replace = TRUE),
    BUILT_FORM = sample(c("Detached", "Semi-Detached", "Terraced", "End-Terrace", NA), 1000, replace = TRUE),
    TOTAL_FLOOR_AREA = rnorm(1000, 100, 20),
    NUMBER_HABITABLE_ROOMS = rpois(1000, 5),
    lodgement_year = sample(2010:2023, 1000, replace = TRUE),
    bad_EPC = sample(0:1, 1000, replace = TRUE),
    source = "Dummy",
    postcode_sector = sample(paste0("AB", 1:10), 1000, replace = TRUE),
    LOCAL_AUTHORITY_LABEL = sample(paste0("LA_", LETTERS[1:5]), 1000, replace = TRUE)
  )
} else {
  load(load_path)
}

# Ensure EPC_matched_combined is a data.table
if (!is.data.table(EPC_matched_combined)) {
  setDT(EPC_matched_combined)
}
# Display a brief summary of the loaded data
print(head(EPC_matched_combined, 3))
cat("\nDimensions of loaded data:", dim(EPC_matched_combined), "\n")
```

## Clean `MAIN_FUEL` Variable

The `MAIN_FUEL` variable requires cleaning and standardization.

```{r clean_main_fuel}
# Ensure it's a data.table if not already
setDT(EPC_matched_combined) 

EPC_matched_combined[
  , MAIN_FUEL_CLEAN := trimws(MAIN_FUEL)
][
  MAIN_FUEL_CLEAN == "", MAIN_FUEL_CLEAN := NA_character_
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := gsub("\\s*[–-]\\s*this is for backwards compatibility only and should not be used$", 
                          "", MAIN_FUEL_CLEAN, ignore.case = TRUE)
]

EPC_matched_combined[
  grepl("^To be used only when", MAIN_FUEL_CLEAN, ignore.case = TRUE),
  MAIN_FUEL_CLEAN := NA_character_
]

EPC_matched_combined[
  MAIN_FUEL_CLEAN %in% c("INVALID!", "NO DATA!"),
  MAIN_FUEL_CLEAN := NA_character_
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := gsub("\\s*\\((community|not community)\\)$", 
                          "", MAIN_FUEL_CLEAN, ignore.case = TRUE)
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := gsub("^(Gas|Electricity|Oil):\\s*", 
                          "", MAIN_FUEL_CLEAN, ignore.case = TRUE)
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := tolower(MAIN_FUEL_CLEAN)
]

# Consolidate MAIN_FUEL categories
EPC_matched_combined[
  , MAIN_FUEL_FINAL := fcase(
    grepl("^anthracite$", MAIN_FUEL_CLEAN), "coal",
    grepl("^appliances able to use mineral oil or liquid biofuel$", MAIN_FUEL_CLEAN), "dual_fuel",
    grepl("^b30[dk]$", MAIN_FUEL_CLEAN), "biomass",
    grepl("^(electricity displaced from grid|electricity, unspecified tariff)$", MAIN_FUEL_CLEAN), "electricity",
    grepl("^oil$", MAIN_FUEL_CLEAN), "heating_oil",
    grepl("^mains gas$", MAIN_FUEL_CLEAN), "mains_gas",
    grepl("lpg", MAIN_FUEL_CLEAN), "lpg",
    grepl("heating oil|rapeseed oil", MAIN_FUEL_CLEAN), "heating_oil",
    grepl("coal", MAIN_FUEL_CLEAN), "coal", # Includes "house coal", "smokeless coal"
    grepl("wood|pellet|chip", MAIN_FUEL_CLEAN), "wood",
    grepl("biomass|biodiesel|biogas", MAIN_FUEL_CLEAN), "biomass",
    grepl("^electricity$", MAIN_FUEL_CLEAN), "electricity",
    # grepl("dual fuel", MAIN_FUEL_CLEAN), "dual_fuel", # Too rare a categories in this sample
    # !is.na(MAIN_FUEL_CLEAN), "other",
    default = NA_character_
  )
]
cat("\nFrequency table for MAIN_FUEL_FINAL (including NAs):\n")
print(table(EPC_matched_combined$MAIN_FUEL_FINAL, useNA="ifany"))
```

# Treatment Definitions
The treatments are combinations of coarse proprietorship (for-profit, non-profit, public) and registration country of the landlord. 

Following treatments are proposed: (1) UK for-profit firms `treat_uk_forprofit`; (2) non-UK for-profit firms `treat_foreign_forprofit`; (3) tax haven registred entities, regardless whether for or not-for profit `treat_tax_haven`; (4) UK public sector `treat_uk_public`; (5) [unused] all for-profit firms `treat_all_forprofit`. 

NOTE: I am somewhat surprised that the overwhelming majority of foreign owners are registered (at least partially) in tax havens - since for a property to have a "tax haven" flag, at least one of its proprietors must be in a tax haven. 


```{r treatment_definitions, echo=TRUE}
# Treatment definition 1 - UK For-Profits
EPC_matched_combined[, treat_uk_forprofit  
  := as.integer(grepl("UNITED KINGDOM", country_incorporated_1, ignore.case = TRUE) & 
  grepl("For-Profit", coarse_proprietorship, ignore.case = TRUE))]

# Treatment definition 2 - Non - UK For-Profits
EPC_matched_combined[, treat_foreign_forprofit := as.integer(
  grepl("For-Profit", coarse_proprietorship, ignore.case = TRUE) &
  !grepl("UNITED KINGDOM", country_incorporated_1, ignore.case = TRUE)
)]

# Treatment definition 3 - Tax Haven
EPC_matched_combined[, treat_tax_haven := as.integer(country_incorporated_tax_haven == 1)]

# Treatment definition 4 - UK Public Sector
EPC_matched_combined[, treat_uk_public 
  := as.integer(grepl("Public Sector", coarse_proprietorship, ignore.case = TRUE))]

# Treatment definition 5 - All For Profit
EPC_matched_combined[, treat_all_forprofit 
  := as.integer(grepl("For-Profit", coarse_proprietorship, ignore.case = TRUE))]

cat("Summary of treatment variables:\n")
print(summary(EPC_matched_combined[, .(treat_uk_forprofit, treat_foreign_forprofit, treat_tax_haven, treat_uk_public, treat_all_forprofit)]))
```{r treatment_tables}
# Only showing a subset of tables for brevity in this refactored example
cat("Cross-tabulation: Tax Haven Status vs Coarse Proprietorship\n")
print(table(EPC_matched_combined$country_incorporated_tax_haven, EPC_matched_combined$coarse_proprietorship, useNA = "ifany"))
```

# Matching Procedure
Propensity score and exact matching variables are taken from "Regulatory barriers to climate action: evidence from conservation areas in England": Exact matching on `tenure` (leasehold/freehold), construction age band, property type, built form (detached/semi-detached/...), main fuel (see note 1 and code above). Propensity score matching (here: nearest neighbour / quick/ but could be others - see note 2) is preformed on total floor area, number of habitable rooms and EPC certificate lodgement year. 

The matching is performed within local authorities, and then the lists get amalgamated together. The local authorities with less than 5 treated or 15 control observations should be skipped. In the end, when regressions are ran, for the benefit of allowing matched-pair fixed effects, the `subclass` variable, created by `matchit` as an index of the matched pair is concatenated with the local authority ID from the EPC dataset, so we actually get unique matched pairs (with two observations within each concatenated ID, as expected). 

The output for each treatment variable includes: the code for the matching, matching balance assesment using a balance table and a love plot, the regression of the relevant treatment on bad_EPC with matched pair fixed effects. 

NOTE 1 : The `FUEL_TYPE` variable, even coarsened as above, significantly reduces the size of the treated cohort. This becomes a more significant problem with matching for foreign for-profit companies later on -- leaving just dozens of treated observation in some cases. 

NOTE 2: The sections of the code for other matching methods can be commented-uncommented as necessary, the matching evaluation code (tables / plots) should work fine. See comments in code. TODO: A more elegant functional programming approach would avoid duplicating all the code everything. 

# Defining Functions

```{r define_psm_functions, echo=TRUE, cache=FALSE}
# Function to perform matching
perform_matching <- function(input_dt, 
                             treatment_var, 
                             analysis_id, 
                             prop_score_covs, 
                             exact_vars,
                             subset_condition_expr = NULL,
                             outcome_var = "bad_EPC", # Keep for consistency, though not used directly in matching
                             min_treated_la = 5,
                             min_control_la = 15,
                             verbose = FALSE) {

  cat(paste0("\n--- Performing Matching for: ", analysis_id, " ---\n"))
  
  # Apply subset condition if provided
  if (!is.null(subset_condition_expr)) {
    current_data <- input_dt[eval(subset_condition_expr)]
    cat(paste0("Subset applied for ", analysis_id, ". Rows after subset: ", nrow(current_data), "\n"))
  } else {
    current_data <- copy(input_dt)
  }
  
  all_nec_vars <- c("source", outcome_var, treatment_var, prop_score_covs, exact_vars, "postcode_sector", "LOCAL_AUTHORITY_LABEL")
  
  missing_cols <- setdiff(all_nec_vars, names(current_data))
  if (length(missing_cols) > 0) {
    stop(paste("Missing columns for analysis", analysis_id, ":", paste(missing_cols, collapse=", ")))
  }
  
  combined_nomiss <- current_data[complete.cases(current_data[, ..all_nec_vars])]

  if (nrow(combined_nomiss) == 0) {
    cat("No complete cases for matching in analysis:", analysis_id, "\nSkipping matching.\n")
    return(list(mdata_nearest = data.table(), mdata_quick = data.table(), combined_nomiss = data.table()))
  }
  
  for (col in exact_vars) {
    if (!is.factor(combined_nomiss[[col]])) {
      combined_nomiss[, (col) := as.factor(get(col))]
    }
  }

  unique_las <- unique(combined_nomiss$LOCAL_AUTHORITY_LABEL)
  mdata_list_nearest <- list()
  mdata_list_quick <- list()

  for (la in unique_las) {
    la_data <- combined_nomiss[LOCAL_AUTHORITY_LABEL == la]
    if (verbose) cat("\nProcessing LA:", la, "- Total rows:", nrow(la_data), "\n")
    
    n_treated <- sum(la_data[[treatment_var]] == 1, na.rm = TRUE)
    n_control <- sum(la_data[[treatment_var]] == 0, na.rm = TRUE)
    if (verbose) cat("Treated units:", n_treated, "Control units:", n_control, "\n")
    
    if (n_treated < min_treated_la || n_control < min_control_la) {
      if (verbose) cat("Skipping LA", la, "due to insufficient treated/control units.\n")
      next
    }
    
    ps_formula_str <- paste(treatment_var, "~", paste(prop_score_covs, collapse = " + "))
    ps_formula <- as.formula(ps_formula_str)
    exact_formula_str <- paste("~", paste(exact_vars, collapse = " + "))
    exact_formula_la <- as.formula(exact_formula_str)
    
    tryCatch({
      match_obj_nearest <- matchit(ps_formula, data = la_data, method = "nearest",
                                   distance = "glm", exact = exact_formula_la)
      mdata_list_nearest[[la]] <- match.data(match_obj_nearest)
    }, error = function(e) cat("Error Nearest matching LA:", la, "-", e$message, "\n"))
    
    tryCatch({
      match_obj_quick <- matchit(ps_formula, data = la_data, method = "quick", 
                                 exact = exact_formula_la)
      mdata_list_quick[[la]] <- match.data(match_obj_quick)
    }, error = function(e) cat("Error Quick matching LA:", la, "-", e$message, "\n"))
  }

  mdata_llc_nearest_by_la <- rbindlist(mdata_list_nearest, use.names = TRUE, fill = TRUE, idcol = "original_LA_for_debug")
  mdata_llc_quick_by_la <- rbindlist(mdata_list_quick, use.names = TRUE, fill = TRUE, idcol = "original_LA_for_debug")
  
  cat(paste0("Matching complete for ", analysis_id, ". Nearest matched N=", nrow(mdata_llc_nearest_by_la), ", Quick matched N=", nrow(mdata_llc_quick_by_la),"\n"))
  
  return(list(
    mdata_nearest = mdata_llc_nearest_by_la, 
    mdata_quick = mdata_llc_quick_by_la,
    combined_nomiss = combined_nomiss # This is the pre-matching data used for this specific analysis (subsetted if applicable)
  ))
}

# Function to generate balance tables
generate_balance_tables <- function(matching_output, 
                                    treatment_var, 
                                    analysis_id, 
                                    prop_score_covs, 
                                    exact_vars) {
  
  cat(paste0("\n## Balance Assessment Tables for ", analysis_id, "\n"))
  
  mdata_nearest <- matching_output$mdata_nearest
  mdata_quick <- matching_output$mdata_quick
  combined_nomiss_for_analysis <- matching_output$combined_nomiss # Use the combined_nomiss specific to this analysis

  balance_formula_terms <- c(prop_score_covs, sapply(exact_vars, function(v) paste0("factor(", v, ")")))
  balance_formula_str <- paste(treatment_var, "~", paste(balance_formula_terms, collapse = " + "))
  balance_formula <- as.formula(balance_formula_str)
  
  bal_tabs <- list()

  # Unadjusted/Baseline
  if (nrow(combined_nomiss_for_analysis) > 0) {
    tryCatch({
      bal_tabs$Unadjusted <- bal.tab(balance_formula, data = combined_nomiss_for_analysis,
                                     treat = treatment_var,
                                     s.d.denom = "pooled", binary = "std", disp.means = TRUE)
      cat("\n### Balance Table: Unadjusted\n")
      balance_df_unadj <- as.data.frame(bal_tabs$Unadjusted$Balance)
      if (nrow(balance_df_unadj) > 0) {
          print(knitr::kable(balance_df_unadj, caption = paste(analysis_id, ": Balance - Unadjusted"), digits = 3) %>%
                kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE))
          if (!is.null(bal_tabs$Unadjusted$Observations)) {
             cat("\n#### Observations (Unadjusted):\n")
             print(knitr::kable(bal_tabs$Unadjusted$Observations))
          }
      } else { cat("No balance info for Unadjusted.\n")}
    }, error = function(e) cat("Error bal.tab Unadjusted:", e$message, "\n"))
  } else { cat("No data for Unadjusted balance table in", analysis_id, "\n")}

  # Nearest neighbor
  if (nrow(mdata_nearest) > 0) {
    tryCatch({
      bal_tabs$Nearest <- bal.tab(balance_formula, data = mdata_nearest, 
                                  weights = "weights", method = "matching", 
                                  s.d.denom = "pooled", un = TRUE, binary = "std", disp.matched = TRUE, disp.means = TRUE)
      cat("\n### Balance Table: Nearest Neighbor Matching\n")
      balance_df_nearest <- as.data.frame(bal_tabs$Nearest$Balance)
      if (nrow(balance_df_nearest) > 0) {
          print(knitr::kable(balance_df_nearest, caption = paste(analysis_id, ": Balance - Nearest Neighbor"), digits = 3) %>%
                kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE))
          if (!is.null(bal_tabs$Nearest$Observations)) {
             cat("\n#### Observations (Nearest Neighbor):\n")
             print(knitr::kable(bal_tabs$Nearest$Observations))
          }
      } else { cat("No balance info for Nearest.\n")}
    }, error = function(e) cat("Error bal.tab Nearest:", e$message, "\n"))
  } else { cat("No data for Nearest Neighbor balance table in", analysis_id, "\n")}
  
  # Quick matching
  if (nrow(mdata_quick) > 0) {
    tryCatch({
      bal_tabs$Quick <- bal.tab(balance_formula, data = mdata_quick, 
                                weights = "weights", method = "matching", 
                                s.d.denom = "pooled", un = TRUE, binary = "std", disp.matched = TRUE, disp.means = TRUE)
      cat("\n### Balance Table: Quick Matching\n")
      balance_df_quick <- as.data.frame(bal_tabs$Quick$Balance)
       if (nrow(balance_df_quick) > 0) {
          print(knitr::kable(balance_df_quick, caption = paste(analysis_id, ": Balance - Quick Matching"), digits = 3) %>%
                kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE))
          if (!is.null(bal_tabs$Quick$Observations)) {
             cat("\n#### Observations (Quick Matching):\n")
             print(knitr::kable(bal_tabs$Quick$Observations))
          }
      } else { cat("No balance info for Quick.\n")}
    }, error = function(e) cat("Error bal.tab Quick:", e$message, "\n"))
  } else { cat("No data for Quick Matching balance table in", analysis_id, "\n")}
  
  return(bal_tabs)
}

# Function to generate Love plots
generate_love_plots <- function(bal_tabs_list, analysis_id) {
  cat(paste0("\n## Love Plots for ", analysis_id, "\n"))
  
  if (!is.null(bal_tabs_list$Quick) && length(bal_tabs_list$Quick) > 0) {
    tryCatch({
      lpq <- love.plot(bal_tabs_list$Quick, threshold = .1, abs = TRUE, line = TRUE, stars = "std",
                       title = paste(analysis_id, ": Covariate Balance (Quick Matching)"), var.order = "unadjusted")
      print(lpq)
    }, error = function(e) cat("Error generating Love Plot (Quick) for", analysis_id, ":", e$message, "\n"))
  } else { cat("Quick matching balance data not available for Love Plot in", analysis_id, ".\n") }

  if (!is.null(bal_tabs_list$Nearest) && length(bal_tabs_list$Nearest) > 0) {
     tryCatch({
        lpn <- love.plot(bal_tabs_list$Nearest, threshold = .1, abs = TRUE, line = TRUE, stars = "std",
                         title = paste(analysis_id, ": Covariate Balance (Nearest Neighbor)"), var.order = "unadjusted")
        print(lpn)
     }, error = function(e) cat("Error generating Love Plot (Nearest) for", analysis_id, ":", e$message, "\n"))
  } else { cat("Nearest Neighbor matching balance data not available for Love Plot in", analysis_id, ".\n") }
}

# Define common variables for PSM
common_exact_vars <- c("tenure", "CONSTRUCTION_AGE_BAND", "PROPERTY_TYPE", "BUILT_FORM", "MAIN_FUEL_FINAL")
common_prop_score_covs <- c("TOTAL_FLOOR_AREA", "NUMBER_HABITABLE_ROOMS", "lodgement_year")
outcome_variable <- "bad_EPC"
```

# PSM Analysis 1: UK For-Profits (`treat_uk_forprofit`)
Treatment: UK for profit; Control: Otherwise

```{r psm1_matching_balance_plots, results='asis', fig.show='hold', cache=FALSE}
analysis_id_1 <- "PSM1_UK_ForProfit"
treatment_var_1 <- "treat_uk_forprofit"

# Perform matching
matching_results_1 <- perform_matching(
  input_dt = EPC_matched_combined,
  treatment_var = treatment_var_1,
  analysis_id = analysis_id_1,
  prop_score_covs = common_prop_score_covs,
  exact_vars = common_exact_vars,
  outcome_var = outcome_variable 
)

# Generate balance tables
bal_tabs_1 <- generate_balance_tables(
  matching_output = matching_results_1,
  treatment_var = treatment_var_1,
  analysis_id = analysis_id_1,
  prop_score_covs = common_prop_score_covs,
  exact_vars = common_exact_vars
)

# Generate Love plots
generate_love_plots(
  bal_tabs_list = bal_tabs_1,
  analysis_id = analysis_id_1
)
```

## Regression Analysis for `r I(analysis_id_1)`

```{r psm1_regression, echo=TRUE}
cat("\n## Regression Analysis for", analysis_id_1, "\n")
cat("Treatment:", treatment_var_1, "; Control: Otherwise (within matched sample - Nearest Neighbor)\n")

mdata_reg_1 <- matching_results_1$mdata_nearest
if (nrow(mdata_reg_1) > 0) {
  reg_formula_simple_str <- paste(outcome_variable, "~", treatment_var_1)
  m_simple_1 <- feols(as.formula(reg_formula_simple_str), data = mdata_reg_1)
  cat("\n### Regression without fixed effects:\n")
  print(summary(m_simple_1))
  
  if ("subclass" %in% names(mdata_reg_1)) {
    mdata_reg_1[, LOCAL_AUTHORITY_SUBCLASS := paste(LOCAL_AUTHORITY_LABEL, subclass, sep = "_")]
    reg_formula_fe_str <- paste(outcome_variable, "~", treatment_var_1, "| LOCAL_AUTHORITY_SUBCLASS")
    m_fe_1 <- feols(as.formula(reg_formula_fe_str), data = mdata_reg_1)
    cat("\n### Regression with LOCAL_AUTHORITY_SUBCLASS fixed effects:\n")
    print(summary(m_fe_1))
  } else {
    cat("\n'subclass' column not found. Using LOCAL_AUTHORITY_LABEL as fixed effect instead:\n")
    reg_formula_la_fe_str <- paste(outcome_variable, "~", treatment_var_1, "| LOCAL_AUTHORITY_LABEL")
    m_la_fe_1 <- feols(as.formula(reg_formula_la_fe_str), data = mdata_reg_1)
    print(summary(m_la_fe_1))
  }
} else {
  cat("No matched data available for regression analysis for", analysis_id_1, "\n")
}
```

# PSM Analysis 2: Non-UK For-Profits (`treat_foreign_forprofit`)
Treatment: Non-UK for-profit; Control: Otherwise
```{r psm2_matching_balance_plots, results='asis', fig.show='hold', cache=FALSE}
analysis_id_2 <- "PSM2_Foreign_ForProfit"
treatment_var_2 <- "treat_foreign_forprofit"

matching_results_2 <- perform_matching(
  input_dt = EPC_matched_combined,
  treatment_var = treatment_var_2,
  analysis_id = analysis_id_2,
  prop_score_covs = common_prop_score_covs,
  exact_vars = common_exact_vars,
  outcome_var = outcome_variable
)
bal_tabs_2 <- generate_balance_tables(matching_results_2, treatment_var_2, analysis_id_2, common_prop_score_covs, common_exact_vars)
generate_love_plots(bal_tabs_2, analysis_id_2)
```


## Regression Analysis for `r I(analysis_id_2)`


```{r psm2_regression, echo=TRUE}
cat("\n## Regression Analysis for", analysis_id_2, "\n")
cat("Treatment:", treatment_var_2, "; Control: Otherwise (within matched sample - Nearest Neighbor)\n")
mdata_reg_2 <- matching_results_2$mdata_nearest
if (nrow(mdata_reg_2) > 0) {
  # ... (regression code similar to PSM1)
  reg_formula_simple_str <- paste(outcome_variable, "~", treatment_var_2)
  m_simple_2 <- feols(as.formula(reg_formula_simple_str), data = mdata_reg_2)
  print(summary(m_simple_2))
  if ("subclass" %in% names(mdata_reg_2)) {
    mdata_reg_2[, LOCAL_AUTHORITY_SUBCLASS := paste(LOCAL_AUTHORITY_LABEL, subclass, sep = "_")]
    reg_formula_fe_str <- paste(outcome_variable, "~", treatment_var_2, "| LOCAL_AUTHORITY_SUBCLASS")
    m_fe_2 <- feols(as.formula(reg_formula_fe_str), data = mdata_reg_2)
    print(summary(m_fe_2))
  } else {
    reg_formula_la_fe_str <- paste(outcome_variable, "~", treatment_var_2, "| LOCAL_AUTHORITY_LABEL")
    m_la_fe_2 <- feols(as.formula(reg_formula_la_fe_str), data = mdata_reg_2)
    print(summary(m_la_fe_2))
  }
} else { cat("No matched data for regression in", analysis_id_2, "\n") }
```

# PSM Analysis 3a: UK for profit (`treat_uk_forprofit`) (within For-Profits)
Treatment: UK for-profit; Control: all other for-profits (i.e., non-UK for-profits)
```{r psm3a_matching_balance_plots, results='asis', fig.show='hold', cache=FALSE}
analysis_id_3a <- "PSM3a_UK_vs_Foreign_FP_within_ForProfits"
treatment_var_3a <- "treat_uk_forprofit" # Treatment is UK FP (1) vs Foreign FP (0)

matching_results_3a <- perform_matching(
  input_dt = EPC_matched_combined,
  treatment_var = treatment_var_3a,
  analysis_id = analysis_id_3a,
  prop_score_covs = common_prop_score_covs,
  exact_vars = common_exact_vars,
  subset_condition_expr = expr(coarse_proprietorship == "For-Profit"),
  outcome_var = outcome_variable
)
bal_tabs_3a <- generate_balance_tables(matching_results_3a, treatment_var_3a, analysis_id_3a, common_prop_score_covs, common_exact_vars)
generate_love_plots(bal_tabs_3a, analysis_id_3a)
```


## Regression Analysis for `r I(analysis_id_3a)`


```{r psm3a_regression, echo=TRUE}
cat("\n## Regression Analysis for", analysis_id_3a, "\n")
cat("Treatment:", treatment_var_3a, "; Control: Foreign For-Profit (within matched sample - Nearest Neighbor)\n")
mdata_reg_3a <- matching_results_3a$mdata_nearest
if (nrow(mdata_reg_3a) > 0) {
  # ... (regression code similar to PSM1)
  reg_formula_simple_str <- paste(outcome_variable, "~", treatment_var_3a)
  m_simple_3a <- feols(as.formula(reg_formula_simple_str), data = mdata_reg_3a)
  print(summary(m_simple_3a))
  if ("subclass" %in% names(mdata_reg_3a)) {
    mdata_reg_3a[, LOCAL_AUTHORITY_SUBCLASS := paste(LOCAL_AUTHORITY_LABEL, subclass, sep = "_")]
    reg_formula_fe_str <- paste(outcome_variable, "~", treatment_var_3a, "| LOCAL_AUTHORITY_SUBCLASS")
    m_fe_3a <- feols(as.formula(reg_formula_fe_str), data = mdata_reg_3a)
    print(summary(m_fe_3a))
  } else {
    reg_formula_la_fe_str <- paste(outcome_variable, "~", treatment_var_3a, "| LOCAL_AUTHORITY_LABEL")
    m_la_fe_3a <- feols(as.formula(reg_formula_la_fe_str), data = mdata_reg_3a)
    print(summary(m_la_fe_3a))
  }
} else { cat("No matched data for regression in", analysis_id_3a, "\n") }
```

# PSM Analysis 3b: Tax Haven (`treat_tax_haven`) (within For-Profits)
Treatment: tax haven for-profit; Control: all other (non-tax haven) for-profits

```{r psm3b_matching_balance_plots, results='asis',  fig.show='hold', cache=FALSE}
analysis_id_3b <- "PSM3b_TaxHaven_vs_NonTaxHaven_FP_within_ForProfits"
treatment_var_3b <- "treat_tax_haven" # Treatment is Tax Haven FP (1) vs Non-Tax Haven FP (0)

matching_results_3b <- perform_matching(
  input_dt = EPC_matched_combined,
  treatment_var = treatment_var_3b,
  analysis_id = analysis_id_3b,
  prop_score_covs = common_prop_score_covs,
  exact_vars = common_exact_vars,
  subset_condition_expr = expr(coarse_proprietorship == "For-Profit"),
  outcome_var = outcome_variable
)
bal_tabs_3b <- generate_balance_tables(matching_results_3b, treatment_var_3b, analysis_id_3b, common_prop_score_covs, common_exact_vars)
generate_love_plots(bal_tabs_3b, analysis_id_3b)
```


## Regression Analysis for `r I(analysis_id_3b)`


```{r psm3b_regression, echo=TRUE}
cat("\n## Regression Analysis for", analysis_id_3b, "\n")
cat("Treatment:", treatment_var_3b, "; Control: Non-Tax Haven For-Profit (within matched sample - Nearest Neighbor)\n")
mdata_reg_3b <- matching_results_3b$mdata_nearest
if (nrow(mdata_reg_3b) > 0) {
  # ... (regression code similar to PSM1)
  reg_formula_simple_str <- paste(outcome_variable, "~", treatment_var_3b)
  m_simple_3b <- feols(as.formula(reg_formula_simple_str), data = mdata_reg_3b)
  print(summary(m_simple_3b))
  if ("subclass" %in% names(mdata_reg_3b)) {
    mdata_reg_3b[, LOCAL_AUTHORITY_SUBCLASS := paste(LOCAL_AUTHORITY_LABEL, subclass, sep = "_")]
    reg_formula_fe_str <- paste(outcome_variable, "~", treatment_var_3b, "| LOCAL_AUTHORITY_SUBCLASS")
    m_fe_3b <- feols(as.formula(reg_formula_fe_str), data = mdata_reg_3b)
    print(summary(m_fe_3b))
  } else {
    reg_formula_la_fe_str <- paste(outcome_variable, "~", treatment_var_3b, "| LOCAL_AUTHORITY_LABEL")
    m_la_fe_3b <- feols(as.formula(reg_formula_la_fe_str), data = mdata_reg_3b)
    print(summary(m_la_fe_3b))
  }
} else { cat("No matched data for regression in", analysis_id_3b, "\n") }
```


# PSM Analysis 4: UK Public Sector (`treat_uk_public`)
Treatment: UK public sector (mostly councils); Control: otherwise


```{r psm4_matching_balance_plots, results='asis', fig.show='hold', cache=FALSE}
analysis_id_4 <- "PSM4_UK_Public_Sector"
treatment_var_4 <- "treat_uk_public"

matching_results_4 <- perform_matching(
  input_dt = EPC_matched_combined,
  treatment_var = treatment_var_4,
  analysis_id = analysis_id_4,
  prop_score_covs = common_prop_score_covs,
  exact_vars = common_exact_vars,
  outcome_var = outcome_variable
)
bal_tabs_4 <- generate_balance_tables(matching_results_4, treatment_var_4, analysis_id_4, common_prop_score_covs, common_exact_vars)
generate_love_plots(bal_tabs_4, analysis_id_4)
```


## Regression Analysis for `r I(analysis_id_4)`
NB! Quick matching results used here.

```{r psm4_regression, echo=TRUE}
cat("\n## Regression Analysis for", analysis_id_4, "\n")
cat("Treatment:", treatment_var_4, "; Control: Otherwise (within matched sample - Nearest Neighbor)\n")
mdata_reg_4 <- matching_results_4$mdata_quick
if (nrow(mdata_reg_4) > 0) {
  # ... (regression code similar to PSM1)
  reg_formula_simple_str <- paste(outcome_variable, "~", treatment_var_4)
  m_simple_4 <- feols(as.formula(reg_formula_simple_str), data = mdata_reg_4)
  print(summary(m_simple_4))
  if ("subclass" %in% names(mdata_reg_4)) {
    mdata_reg_4[, LOCAL_AUTHORITY_SUBCLASS := paste(LOCAL_AUTHORITY_LABEL, subclass, sep = "_")]
    reg_formula_fe_str <- paste(outcome_variable, "~", treatment_var_4, "| LOCAL_AUTHORITY_SUBCLASS")
    m_fe_4 <- feols(as.formula(reg_formula_fe_str), data = mdata_reg_4)
    print(summary(m_fe_4))
  } else {
    reg_formula_la_fe_str <- paste(outcome_variable, "~", treatment_var_4, "| LOCAL_AUTHORITY_LABEL")
    m_la_fe_4 <- feols(as.formula(reg_formula_la_fe_str), data = mdata_reg_4)
    print(summary(m_la_fe_4))
  }
} else { cat("No matched data for regression in", analysis_id_4, "\n") }
```

