---
title: "Disconnected Landlords PSM Analysis (Updated Treatment Definitions)"
author: "Dmytro Kunchenko"
date: "2025-06-11"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
# This chunk runs setup code but doesn't show in the document.
# Load required packages
library(fixest)
library(car) 
library(httr) 
library(jsonlite) 
library(data.table)
library(MatchIt)
library(cobalt)
library(optmatch) 
library(Matching) 
library(rgenoud) 
library(marginaleffects)
library(ggplot2)
library(gridExtra) 
library(kableExtra)
library(rlang) # For handling expressions in the function

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,      # Hide R code by default
  cache = FALSE, 
  message = FALSE,   # Suppress messages
  warning = FALSE,   # Suppress warnings
  fig.height = 6,
  fig.width = 10,
  include = TRUE     # Include output (plots, tables) by default
)
```

# Overview

This document outlines the Propensity Score Matching (PSM) analysis for the "Disconnected Landlords" project, with updated treatment definitions based on recent discussions. The analysis now focuses on privately rented properties, using landlords with no corporate ownership records as the control group.

# Data Loading and Preprocessing

## Load Data

First, load the dataset. **Ensure the path to the .RData file is correct.**

```{r load_data, echo=TRUE}
# Load data
# Replace with the correct path if necessary
load_path <- "~/disconnected-landlords-project/EPC_matched_combined.RData" 
# For testing, if the file doesn't exist, create a dummy EPC_matched_combined
if (!file.exists(load_path)) {
  warning(paste("Data file not found at:", load_path, ". Using a minimal dummy dataset for demonstration."))
  EPC_matched_combined <- data.table(
    UPRN = 1:2000,
    MAIN_FUEL = sample(c("mains gas", "electricity", "oil", "Gas: mains gas", "INVALID!", "", "To be used only when other fuel specified"), 2000, replace = TRUE),
    country_incorporated_1 = sample(c("UNITED KINGDOM", "JERSEY", "USA", NA), 2000, replace = TRUE),
    coarse_proprietorship = sample(c("For-Profit", "Non-Profit", "Public Sector", "Individual"), 2000, replace = TRUE),
    country_incorporated_tax_haven = sample(c(0, 1, NA), 2000, replace = TRUE, prob = c(0.7, 0.2, 0.1)),
    TENURE = sample(c("Rented (private)", "Owner-occupied", "Rented (social)", NA), 2000, replace = TRUE),
    CONSTRUCTION_AGE_BAND = sample(c("2000-Present", "1950-1975", "Pre-1900", NA), 2000, replace = TRUE),
    PROPERTY_TYPE = sample(c("House", "Flat", "Bungalow", NA), 2000, replace = TRUE),
    BUILT_FORM = sample(c("Detached", "Semi-Detached", "Terraced", "End-Terrace", NA), 2000, replace = TRUE),
    TOTAL_FLOOR_AREA = rnorm(2000, 100, 20),
    NUMBER_HABITABLE_ROOMS = rpois(2000, 5),
    lodgement_year = sample(2010:2023, 2000, replace = TRUE),
    bad_EPC = sample(0:1, 2000, replace = TRUE, prob = c(0.7, 0.3)),
    source = sample(c("CCOD", "OCOD", "Unknown"), 2000, replace = TRUE, prob = c(0.2, 0.1, 0.7)),
    postcode_sector = sample(paste0("AB", 1:10), 2000, replace = TRUE),
    LOCAL_AUTHORITY_LABEL = sample(paste0("LA_", LETTERS[1:5]), 2000, replace = TRUE)
  )
} else {
  load(load_path)
}

# Ensure EPC_matched_combined is a data.table
if (!is.data.table(EPC_matched_combined)) {
  setDT(EPC_matched_combined)
}
# Display a brief summary of the loaded data
print(head(EPC_matched_combined, 3))
cat("\nDimensions of loaded data:", dim(EPC_matched_combined), "\n")
```

## Clean `MAIN_FUEL` Variable

The `MAIN_FUEL` variable requires cleaning and standardization.

```{r clean_main_fuel}
# Ensure it's a data.table if not already
setDT(EPC_matched_combined) 

EPC_matched_combined[
  , MAIN_FUEL_CLEAN := trimws(MAIN_FUEL)
][
  MAIN_FUEL_CLEAN == "", MAIN_FUEL_CLEAN := NA_character_
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := gsub("\\s*[–-]\\s*this is for backwards compatibility only and should not be used$", 
                          "", MAIN_FUEL_CLEAN, ignore.case = TRUE)
]

EPC_matched_combined[
  grepl("^To be used only when", MAIN_FUEL_CLEAN, ignore.case = TRUE),
  MAIN_FUEL_CLEAN := NA_character_
]

EPC_matched_combined[
  MAIN_FUEL_CLEAN %in% c("INVALID!", "NO DATA!"),
  MAIN_FUEL_CLEAN := NA_character_
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := gsub("\\s*\\((community|not community)\\)$", 
                          "", MAIN_FUEL_CLEAN, ignore.case = TRUE)
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := gsub("^(Gas|Electricity|Oil):\\s*", 
                          "", MAIN_FUEL_CLEAN, ignore.case = TRUE)
]

EPC_matched_combined[
  !is.na(MAIN_FUEL_CLEAN),
  MAIN_FUEL_CLEAN := tolower(MAIN_FUEL_CLEAN)
]

# Consolidate MAIN_FUEL categories
EPC_matched_combined[
  , MAIN_FUEL_FINAL := fcase(
    grepl("^anthracite$", MAIN_FUEL_CLEAN), "coal",
    grepl("^appliances able to use mineral oil or liquid biofuel$", MAIN_FUEL_CLEAN), "dual_fuel",
    grepl("^b30[dk]$", MAIN_FUEL_CLEAN), "biomass",
    grepl("^(electricity displaced from grid|electricity, unspecified tariff)$", MAIN_FUEL_CLEAN), "electricity",
    grepl("^oil$", MAIN_FUEL_CLEAN), "heating_oil",
    grepl("^mains gas$", MAIN_FUEL_CLEAN), "mains_gas",
    grepl("lpg", MAIN_FUEL_CLEAN), "lpg",
    grepl("heating oil|rapeseed oil", MAIN_FUEL_CLEAN), "heating_oil",
    grepl("coal", MAIN_FUEL_CLEAN), "coal", # Includes "house coal", "smokeless coal"
    grepl("wood|pellet|chip", MAIN_FUEL_CLEAN), "wood",
    grepl("biomass|biodiesel|biogas", MAIN_FUEL_CLEAN), "biomass",
    grepl("^electricity$", MAIN_FUEL_CLEAN), "electricity",
    default = NA_character_
  )
]
cat("\nFrequency table for MAIN_FUEL_FINAL (including NAs):\n")
print(table(EPC_matched_combined$MAIN_FUEL_FINAL, useNA="ifany"))
```

# Updated Treatment and Control Definitions

The analysis is now restricted to privately rented properties. The control group is defined as privately rented properties with no CCOD/OCOD record (`source == "Unknown"`).

```{r treatment_definitions, echo=TRUE}
# Filter for properties that are privately rented
EPC_matched_combined <- EPC_matched_combined[TENURE == "Rented (private)"]

# Display a brief summary of the filtered data
cat("\nDimensions of data after filtering for 'Rented (private)':", dim(EPC_matched_combined), "\n")
cat("\nSummary of source variable for private rentals:\n")
print(table(EPC_matched_combined$source, useNA = "ifany"))

# Define new treatment and control variables for each analysis
# A value of 1 indicates treatment, 0 indicates control, and NA for others.
# Using 1L and 0L to ensure integer type, matching NA_integer_

# Analysis 1: UK For-Profits vs. Private Landlords (No CCOD/OCOD)
EPC_matched_combined[, treat_ukforprofit := fcase(
  source == "CCOD" & grepl("For-Profit", coarse_proprietorship, ignore.case = TRUE), 1L,
  source == "Unknown", 0L,
  default = NA_integer_
)]

# Analysis 2: Foreign For-Profits vs. Private Landlords (No CCOD/OCOD)
EPC_matched_combined[, treat_foreignforprofit := fcase(
  grepl("For-Profit", coarse_proprietorship, ignore.case = TRUE) & 
    (source == "OCOD" | (!is.na(country_incorporated_1) & country_incorporated_1 != "UNITED KINGDOM")), 1L,
  source == "Unknown", 0L,
  default = NA_integer_
)]

# Analysis 3: Tax Haven Landlords vs. Private Landlords (No CCOD/OCOD)
EPC_matched_combined[, treat_tax_haven := fcase(
  country_incorporated_tax_haven == 1, 1L,
  source == "Unknown", 0L,
  default = NA_integer_
)]

# Analysis 4: UK Public Sector vs. Private Landlords (No CCOD/OCOD)
EPC_matched_combined[, treat_public := fcase(
  grepl("Public Sector", coarse_proprietorship, ignore.case = TRUE), 1L,
  source == "Unknown", 0L,
  default = NA_integer_
)]

# Summary of the new treatment variables
cat("\nSummary of new treatment variables (1=Treated, 0=Control, NA=Not in comparison):\n")
print(summary(EPC_matched_combined[, .(treat_ukforprofit, treat_foreignforprofit, treat_tax_haven, treat_public)]))
```

# Matching Procedure
Propensity score and exact matching variables are taken from "Regulatory barriers to climate action: evidence from conservation areas in England": Exact matching on `tenure` (leasehold/freehold), construction age band, property type, built form (detached/semi-detached/...), main fuel (see note 1 and code above). Propensity score matching (here: nearest neighbour / quick/ but could be others - see note 2) is preformed on total floor area, number of habitable rooms and EPC certificate lodgement year. 

# Defining Functions
```{r define_psm_functions, echo=TRUE, cache=FALSE}
# Function to perform matching
perform_matching <- function(input_dt, treatment_var, analysis_id, prop_score_covs, exact_vars, outcome_var = "bad_EPC",
                             min_treated_la = 5, min_control_la = 15, verbose = FALSE) {

  cat(paste0("\n--- Performing Matching for: ", analysis_id, " ---\n"))
  
  # Filter the data to include only rows relevant to the current treatment comparison
  current_data <- input_dt[!is.na(get(treatment_var))]

  all_nec_vars <- c("source", outcome_var, treatment_var, prop_score_covs, exact_vars, "postcode_sector", "LOCAL_AUTHORITY_LABEL")
  missing_cols <- setdiff(all_nec_vars, names(current_data))
  
  if (length(missing_cols) > 0) {
    stop(paste("Missing columns for analysis", analysis_id, ":", paste(missing_cols, collapse=", ")))
  }

  combined_nomiss <- current_data[complete.cases(current_data[, ..all_nec_vars])]
  
  if (nrow(combined_nomiss) == 0) {
    cat("No complete cases for matching in analysis:", analysis_id, "\nSkipping matching.\n")
    return(list(mdata_nearest = data.table(), mdata_quick = data.table(), combined_nomiss = data.table()))
  }
  
  for (col in exact_vars) {
    if (!is.factor(combined_nomiss[[col]])) {
      combined_nomiss[, (col) := as.factor(get(col))]
    }
  }

  unique_las <- unique(combined_nomiss$LOCAL_AUTHORITY_LABEL)
  mdata_list_nearest <- list()
  mdata_list_quick <- list()

  for (la in unique_las) {
    la_data <- combined_nomiss[LOCAL_AUTHORITY_LABEL == la]
    
    if (verbose) cat("\nProcessing LA:", la, "- Total rows:", nrow(la_data), "\n")
    
    n_treated <- sum(la_data[[treatment_var]] == 1, na.rm = TRUE)
    n_control <- sum(la_data[[treatment_var]] == 0, na.rm = TRUE)
    
    if (verbose) cat("Treated units:", n_treated, "Control units:", n_control, "\n")

    if (n_treated < min_treated_la || n_control < min_control_la) {
      if (verbose) cat("Skipping LA", la, "due to insufficient treated/control units.\n")
      next
    }
    
    ps_formula_str <- paste(treatment_var, "~", paste(prop_score_covs, collapse = " + "))
    ps_formula <- as.formula(ps_formula_str)
    
    exact_formula_str <- paste("~", paste(exact_vars, collapse = " + "))
    exact_formula_la <- as.formula(exact_formula_str)
    
    tryCatch({
      match_obj_nearest <- matchit(ps_formula, data = la_data, method = "nearest", distance = "glm", exact = exact_formula_la)
      mdata_list_nearest[[la]] <- match.data(match_obj_nearest)
    }, error = function(e) cat("Error Nearest matching LA:", la, "-", e$message, "\n"))
    
    tryCatch({
      match_obj_quick <- matchit(ps_formula, data = la_data, method = "quick", exact = exact_formula_la)
      mdata_list_quick[[la]] <- match.data(match_obj_quick)
    }, error = function(e) cat("Error Quick matching LA:", la, "-", e$message, "\n"))
  }
  
  mdata_llc_nearest_by_la <- rbindlist(mdata_list_nearest, use.names = TRUE, fill = TRUE, idcol = "original_LA_for_debug")
  mdata_llc_quick_by_la <- rbindlist(mdata_list_quick, use.names = TRUE, fill = TRUE, idcol = "original_LA_for_debug")
  
  cat(paste0("Matching complete for ", analysis_id, ". Nearest matched N=", nrow(mdata_llc_nearest_by_la), ", Quick matched N=", nrow(mdata_llc_quick_by_la),"\n"))

  return(list(
    mdata_nearest = mdata_llc_nearest_by_la,
    mdata_quick = mdata_llc_quick_by_la,
    combined_nomiss = combined_nomiss
  ))
}

# Function to generate balance tables
generate_balance_tables <- function(matching_output, treatment_var, analysis_id, prop_score_covs, exact_vars) {
  
  if (nrow(matching_output$mdata_nearest) == 0 && nrow(matching_output$mdata_quick) == 0) {
    cat(paste("\nNo matched data for", analysis_id, "to generate balance tables.\n"))
    return(NULL)
  }

  ps_formula_str <- paste(treatment_var, "~", paste(c(prop_score_covs, exact_vars), collapse = " + "))
  ps_formula <- as.formula(ps_formula_str)
  
  bal_tabs <- list()

  # Unmatched
  bal_tabs$unmatched <- bal.tab(
    ps_formula, 
    data = matching_output$combined_nomiss, 
    estimand = "ATT",
    disp = c("m", "sd"), 
    
  )

  # Nearest Neighbor
  if (nrow(matching_output$mdata_nearest) > 0) {
    bal_tabs$nearest <- bal.tab(
      ps_formula, 
      data = matching_output$mdata_nearest,
      estimand = "ATT",
      disp = c("m", "sd"), 
      
    )
    cat(paste0("\n### Balance Table for ", analysis_id, " (Nearest Neighbor Matching)\n"))
    print(kable(bal_tabs$nearest$Balance, caption = "Balance Table (Nearest Neighbor)") %>% kable_styling())
  }
  
  # Quick Match
  if (nrow(matching_output$mdata_quick) > 0) {
    bal_tabs$quick <- bal.tab(
      ps_formula, 
      data = matching_output$mdata_quick,
      estimand = "ATT",
      disp = c("m", "sd"), 
      
    )
    cat(paste0("\n### Balance Table for ", analysis_id, " (Quick Matching)\n"))
    print(kable(bal_tabs$quick$Balance, caption = "Balance Table (Quick Match)") %>% kable_styling())
  }
  
  return(bal_tabs)
}


# Function to generate Love plots - CORRECTED
generate_love_plots <- function(bal_tabs_list, analysis_id) {
  cat(paste0("\n## Love Plots for ", analysis_id, "\n"))
  
  if (is.null(bal_tabs_list)) {
    cat("Balance table list is NULL for", analysis_id, ". Skipping Love plots.\n")
    return()
  }
  
  if (!is.null(bal_tabs_list$quick)) {
    tryCatch({
      lpq <- love.plot(bal_tabs_list$quick, threshold = .1, abs = TRUE, line = TRUE, stars = "std",
                           title = paste(analysis_id, ": Covariate Balance (Quick Matching)"), var.order = "unadjusted")
      print(lpq)
    }, error = function(e) cat("Error generating Love Plot (Quick) for", analysis_id, ":", e$message, "\n"))
  } else { cat("Quick matching balance data not available for Love Plot in", analysis_id, ".\n") }

  if (!is.null(bal_tabs_list$nearest)) {
     tryCatch({
       lpn <- love.plot(bal_tabs_list$nearest, threshold = .1, abs = TRUE, line = TRUE, stars = "std",
                          title = paste(analysis_id, ": Covariate Balance (Nearest Neighbor)"), var.order = "unadjusted")
       print(lpn)
     }, error = function(e) cat("Error generating Love Plot (Nearest) for", analysis_id, ":", e$message, "\n"))
  } else { cat("Nearest Neighbor matching balance data not available for Love Plot in", analysis_id, ".\n") }
}



# Function to test the significance of covariate balance
test_balance_significance <- function(matched_data, unmatched_data, treatment_var, covariates) {
  if (nrow(matched_data) == 0 || nrow(unmatched_data) == 0) {
    cat("Not enough data to test balance significance.\n")
    return(NULL)
  }
  
  # Create a data.frame to store results
  balance_results <- data.frame(
    Covariate = character(),
    P_Value_Unmatched = numeric(),
    P_Value_Matched = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (cov in covariates) {
    formula_obj <- as.formula(paste(cov, "~", treatment_var))
    
    # Test on unmatched data
    p_unmatched <- tryCatch({
      model_unmatched <- feols(formula_obj, data = unmatched_data, se = "hetero")
      summary(model_unmatched)$coeftable[treatment_var, "Pr(>|t|)"]
    }, error = function(e) NA)
    
    # Test on matched data (weighted)
    p_matched <- tryCatch({
      model_matched <- feols(formula_obj, data = matched_data, weights = ~weights, se = "hetero")
      summary(model_matched)$coeftable[treatment_var, "Pr(>|t|)"]
    }, error = function(e) NA)

    # Store results
    balance_results <- rbind(balance_results, data.frame(
      Covariate = cov,
      P_Value_Unmatched = p_unmatched,
      P_Value_Matched = p_matched
    ))
  }
  
  return(balance_results)
}

# UPDATED: Function to run regression analysis with and without optional controls
run_regression_analysis <- function(matched_data, outcome_var, treatment_var, analysis_id, control_vars = NULL) {
  cat("\n## Regression Analysis for", analysis_id, "\n")
  cat("Treatment:", treatment_var, "; Control: Otherwise (within matched sample)\n")

  if (is.null(matched_data) || nrow(matched_data) == 0) {
    cat("No matched data available for regression analysis for", analysis_id, "\n")
    return(invisible(NULL))
  }

  # --- Setup common elements ---
  use_weights <- "weights" %in% names(matched_data)
  weight_formula <- if (use_weights) ~weights else NULL
  weight_cat <- if (use_weights) "Weighted" else "Unweighted"

  if ("subclass" %in% names(matched_data)) {
    # Ensure the combined FE variable is a factor
    if (!is.factor(matched_data$subclass)) matched_data[, subclass := as.factor(subclass)]
    if (!is.factor(matched_data$LOCAL_AUTHORITY_LABEL)) matched_data[, LOCAL_AUTHORITY_LABEL := as.factor(LOCAL_AUTHORITY_LABEL)]
    # Use interaction() to create a robust fixed effect from two variables
    matched_data[, LOCAL_AUTHORITY_SUBCLASS := interaction(LOCAL_AUTHORITY_LABEL, subclass, drop = TRUE)]
    fe_str <- "| LOCAL_AUTHORITY_SUBCLASS"
    fe_cat <- "with LOCAL_AUTHORITY_SUBCLASS fixed effects"
  } else {
    fe_str <- "| LOCAL_AUTHORITY_LABEL"
    fe_cat <- "with LOCAL_AUTHORITY_LABEL fixed effects ('subclass' not found)"
  }

  # --- Regressions WITHOUT controls ---
  cat(paste0("\n\n### --- Regressions WITHOUT controls ---\n"))
  cat(paste0("\n### ", weight_cat, " regression\n"))
  formula_rhs_uncontrolled <- treatment_var
  
  # Model 1: Simple (no FE)
  reg_formula_simple_unc <- as.formula(paste(outcome_var, "~", formula_rhs_uncontrolled))
  m_simple_unc <- feols(reg_formula_simple_unc, data = matched_data, weights = weight_formula, se = "hetero")
  print(summary(m_simple_unc))

  # Model 2: With FE
  cat(paste0("\n### ", weight_cat, " regression, ", fe_cat, "\n"))
  reg_formula_fe_unc <- as.formula(paste(outcome_var, "~", formula_rhs_uncontrolled, fe_str))
  m_fe_unc <- feols(reg_formula_fe_unc, data = matched_data, weights = weight_formula, se = "hetero")
  print(summary(m_fe_unc))

  # --- Regressions WITH controls ---
  if (!is.null(control_vars) && length(control_vars) > 0) {
    missing_controls <- setdiff(control_vars, names(matched_data))
    if (length(missing_controls) > 0) {
      cat("\nWarning: The following control variables are not in the matched data and will be ignored:", paste(missing_controls, collapse = ", "), "\n")
      control_vars <- setdiff(control_vars, missing_controls)
    }

    if (length(control_vars) > 0) {
      cat(paste0("\n\n### --- Regressions WITH controls (", paste(control_vars, collapse=", "), ") ---\n"))
      
      cat(paste0("\n### ", weight_cat, " regression with controls\n"))
      formula_rhs_controlled <- paste(c(treatment_var, control_vars), collapse = " + ")

      # Model 3: Simple (no FE) with controls
      reg_formula_simple_con <- as.formula(paste(outcome_var, "~", formula_rhs_controlled))
      m_simple_con <- feols(reg_formula_simple_con, data = matched_data, weights = weight_formula, se = "hetero")
      print(summary(m_simple_con))
      
      # Model 4: With FE and controls
      cat(paste0("\n### ", weight_cat, " regression with controls, ", fe_cat, "\n"))
      reg_formula_fe_con <- as.formula(paste(outcome_var, "~", formula_rhs_controlled, fe_str))
      m_fe_con <- feols(reg_formula_fe_con, data = matched_data, weights = weight_formula, se = "hetero")
      print(summary(m_fe_con))
    }
  }
  
  return(invisible(NULL))
}



# Define common variables for PSM
common_exact_vars <- c("CONSTRUCTION_AGE_BAND", "PROPERTY_TYPE", "BUILT_FORM", "MAIN_FUEL_FINAL")
common_prop_score_covs <- c("TOTAL_FLOOR_AREA", "NUMBER_HABITABLE_ROOMS", "lodgement_year")
outcome_variable <- "bad_EPC"
# NEW: Define regression control variables
regression_controls <- c("TOTAL_FLOOR_AREA", "NUMBER_HABITABLE_ROOMS")

```

# PSM Analysis 1: UK For-Profits vs. Private Landlords
Treatment: UK for-profit; Control: Private landlords (no CCOD/OCOD record)

```{r psm1_analysis, echo=TRUE, cache=TRUE, results='asis', fig.cap="Love Plots for PSM1_UK_vs_Private"}
analysis_id_1 <- "PSM1_UK_vs_Private"
treatment_var_1 <- "treat_ukforprofit"

# Perform matching
matching_results_1 <- perform_matching(EPC_matched_combined, treatment_var_1, analysis_id_1, common_prop_score_covs, common_exact_vars)

# Generate balance tables
balance_tabs_1 <- generate_balance_tables(matching_results_1, treatment_var_1, analysis_id_1, common_prop_score_covs, common_exact_vars)

# Generate Love plots
generate_love_plots(balance_tabs_1, analysis_id_1)

# Test covariate balance significance
if (nrow(matching_results_1$mdata_nearest) > 0) {
  cat("\n### Covariate Balance Significance Test (Nearest Neighbor)\n")
  balance_test_results_1 <- test_balance_significance(
    matched_data = matching_results_1$mdata_nearest,
    unmatched_data = matching_results_1$combined_nomiss,
    treatment_var = treatment_var_1,
    covariates = c(common_prop_score_covs, common_exact_vars)
  )
  if (!is.null(balance_test_results_1)) {
    print(
      kable(balance_test_results_1, caption = "Covariate Balance Significance Test (p-values)", digits = 4)
    )
  }
}
```

## Regression Analysis for `r I(analysis_id_1)`

```{r psm1_regression, echo=TRUE}
# Run regression for analysis 1 using the new function
run_regression_analysis(
  matched_data = matching_results_1$mdata_nearest,
  outcome_var = outcome_variable,
  treatment_var = treatment_var_1,
  analysis_id = analysis_id_1,
  control_vars = regression_controls
)
```

# PSM Analysis 2: Foreign For-Profits vs. Private Landlords
Treatment: Non-UK for-profit; Control: Private landlords (no CCOD/OCOD record)

```{r psm2_analysis, echo=TRUE, cache=TRUE, results='asis', fig.cap="Love Plots for PSM2_Foreign_vs_Private"}
analysis_id_2 <- "PSM2_Foreign_vs_Private"
treatment_var_2 <- "treat_foreignforprofit"

# Perform matching
matching_results_2 <- perform_matching(EPC_matched_combined, treatment_var_2, analysis_id_2, common_prop_score_covs, common_exact_vars)

# Generate balance tables
balance_tabs_2 <- generate_balance_tables(matching_results_2, treatment_var_2, analysis_id_2, common_prop_score_covs, common_exact_vars)

# Generate Love plots
generate_love_plots(balance_tabs_2, analysis_id_2)
```

## Regression Analysis for `r I(analysis_id_2)`

```{r psm2_regression, echo=TRUE}
# Run regression for analysis 2 using the new function
run_regression_analysis(
  matched_data = matching_results_2$mdata_nearest,
  outcome_var = outcome_variable,
  treatment_var = treatment_var_2,
  analysis_id = analysis_id_2,
  control_vars = regression_controls
)
```

# PSM Analysis 3: Tax Haven Landlords vs. Private Landlords
Treatment: Tax Haven registered landlords; Control: Private landlords (no CCOD/OCOD record)

```{r psm3_analysis, echo=TRUE, cache=TRUE, results='asis', fig.cap="Love Plots for PSM3_TaxHaven_vs_Private"}
analysis_id_3 <- "PSM3_TaxHaven_vs_Private"
treatment_var_3 <- "treat_tax_haven"

# Perform matching
matching_results_3 <- perform_matching(EPC_matched_combined, treatment_var_3, analysis_id_3, common_prop_score_covs, common_exact_vars)

# Generate balance tables
balance_tabs_3 <- generate_balance_tables(matching_results_3, treatment_var_3, analysis_id_3, common_prop_score_covs, common_exact_vars)

# Generate Love plots
generate_love_plots(balance_tabs_3, analysis_id_3)
```


## Regression Analysis for `r I(analysis_id_3)`


```{r psm3_regression, echo=TRUE}
# Run regression for analysis 3 using the new function
run_regression_analysis(
  matched_data = matching_results_3$mdata_nearest,
  outcome_var = outcome_variable,
  treatment_var = treatment_var_3,
  analysis_id = analysis_id_3,
  control_vars = regression_controls
)
```

# PSM Analysis 4: UK Public Sector vs. Private Landlords
Treatment: UK Public Sector; Control: Private landlords (no CCOD/OCOD record)

```{r psm4_analysis, echo=TRUE, cache=TRUE, results='asis', fig.cap="Love Plots for PSM4_Public_vs_Private"}
analysis_id_4 <- "PSM4_Public_vs_Private"
treatment_var_4 <- "treat_public"

# Perform matching
matching_results_4 <- perform_matching(EPC_matched_combined, treatment_var_4, analysis_id_4, common_prop_score_covs, common_exact_vars)

# Generate balance tables
balance_tabs_4 <- generate_balance_tables(matching_results_4, treatment_var_4, analysis_id_4, common_prop_score_covs, common_exact_vars)

# Generate Love plots
generate_love_plots(balance_tabs_4, analysis_id_4)
```

## Regression Analysis for `r I(analysis_id_4)`

```{r psm4_regression, echo=TRUE}
# Run regression for analysis 4 using the new function (using Quick Match data as per original script)
run_regression_analysis(
  matched_data = matching_results_4$mdata_quick,
  outcome_var = outcome_variable,
  treatment_var = treatment_var_4,
  analysis_id = analysis_id_4,
  control_vars = regression_controls
)
```


